Tropical Andes IUCN Montane and Lowland forest

### 2025-08-12 code/L0/L0_TropicalAndes_IUCNhabitatClassification.Rmd
Added name, no problems with code

---
title: "Tropical Andes IUCN Montane and Lowland forest"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "Create raster of IUCN habitat classification Forest-Subtropical moist montane and Forest - Subtropical moist lowland for Tropical Andes."
data input: "iucn_habitatclassification_composite_lvl2_ver004.tif"
data output: "TropicalAndes_IUCNHabitat_Forest.GTiff"
date: "2023-07-18"
output: html_document
---

>>>>

---
title: "Tropical Andes IUCN Montane and Lowland forest"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske, Jenna B. Baljunas"
overview: "Create raster of IUCN habitat classification Forest-Subtropical moist montane and Forest - Subtropical moist lowland for Tropical Andes."
data input: "iucn_habitatclassification_composite_lvl2_ver004.tif"
data output: "TropicalAndes_IUCNHabitat_Forest.GTiff"
date: "2023-07-18"
output: html_document
---
